\bf Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test

### 2025-06-12 manuscript/manuscript.tex
touch up

Figures~\ref{fig:qq_n}--\ref{fig:qq_g} show the Quantile-Quantile (Q-Q)
plots of the p-values testing the marginal distribution of the stationary time
series generated from the null hypothesis, created with R packages
\textsl{qqplotr} and \textsl{ggplot2} \citep{qqplotr, ggplot2}. If the
distribution of the p-values is uniform, the points will be aligned with the
diagonal line. The plots suggest that the extent to which the p-values are
uniformly distributed is dependent on the sample size and the level of serial
dependence.
A small sample size like $n = 100$ or $200$ seems adequate when Kendall's
$\tau$ has an absolute value $|\tau| \leq 0.25$. For $|\tau| \geq 0.5$, 
a sample larger than
$n = 200$ seems necessary for the p-values to be uniformly distributed. For
$|\tau| \geq 0.75$, a sample larger than $n = 800$ appears to be
necessary, as the p-values are not aligned with the line in any of the Q-Q
plots. This is not necessarily a cause for concern, as (for normal margins)
a Kendall's $\tau$ of 0.75 corresponds to a $\phi$ of 0.924, which is very high.
Additionally, positive serial dependence appears to misalign the distribution
of the p-values more so than negative serial dependences of the same strength.
Results are very similar for normal and gamma margins.

@@

We evaluated the size and power performance of the NPBB test under automatic
block length selection. The size performance is shown
in Figures~\ref{fig:alt_qq_n} and \ref{fig:alt_qq_g}, which display Q-Q plots
of the $p$-values under the null for Normal and Gamma margins, respectively.
Recall from Figures~\ref{fig:qq_n} and \ref{fig:qq_g} that the cubic root 
setting held its size quite well with small $n$ for $|\tau| \leq 0.25$, whereas
$|\tau| \geq 0.5$ may require $n > 200$, and $|\tau| \geq 0.75$ may 
require $n > 800$.
Similarly, for $|\tau| > 0.5$, the automatic selection
does not hold its size. In addition, the automatic selection actually seems
to have larger deviations from the line for negative $\tau$, which
may be a result of the overly large block sizes. Notably, while the
cubic root setting held its size for $\tau = -0.25$ for small $n$, the automatic
selection does not.
Still, under $\tau = 0$ and $\tau = 0.25$, the method with block size 
selected by
\citet{politis2004automatic} maintains reasonable size for moderately positively
dependent series.

The power results are shown in
Figure~\ref{fig:alt_rr}. For $|\tau| \leq 0.5$, when comparing 
with Figure~\ref{fig:rr}, the two settings exhibit
similar power, with the automatic selection sometimes yielding higher
rejection rates, particularly for smaller negatively dependent samples.
Overall, while the automatic selection from \citet{politis2004automatic}
performs reasonably well in some settings, we recommend caution when using
it under negative~$\tau$ and smaller sample sizes, where maintaining nominal
size may be more challenging. In such cases, it may be sensible to be more
restrictive when setting the final block size --- for example, using
$\min \{\sqrt{n}, \hat l\}$.

>>>>

Figures~\ref{fig:qq_n}--\ref{fig:qq_g} show Quantile-Quantile (Q--Q) plots
of the $p$-values testing the marginal distribution of the stationary time
series generated under the null hypothesis. Figure~\ref{fig:qq_n} corresponds
to the case where the true data generating distribution is $N(8,8)$, and
Figure~\ref{fig:qq_g} corresponds to the case where the true data generating
distribution is $\Gamma(8,1)$. The plots were created using the R packages
\textsl{qqplotr} and \textsl{ggplot2} \citep{qqplotr, ggplot2}. If the
distribution of the p-values is uniform, the points will be aligned with the
diagonal line.

The plots suggest that the extent to which the p-values are uniformly
distributed is dependent on the sample size and the level of serial dependence.
A small sample size like $n = 100$ or $200$ seems adequate when Kendall's
$\tau$ has an absolute value $|\tau| \leq 0.25$. For $|\tau| \geq 0.5$, 
a sample larger than
$n = 200$ seems necessary for the p-values to be uniformly distributed. For
$|\tau| \geq 0.75$, a sample larger than $n = 800$ appears to be
necessary, as the p-values are not aligned with the line in any of the Q-Q
plots. This is not necessarily a cause for concern, as (for normal margins)
a Kendall's $\tau$ of 0.75 corresponds to a $\phi$ of 0.924, which is very high.
Additionally, positive serial dependence appears to misalign the distribution
of the p-values more so than negative serial dependences of the same strength.
Results are very similar for normal and gamma margins.

@@

We evaluated the size and power performance of the NPBB test under automatic
block length selection. The size performance is shown
in Figures~\ref{fig:alt_qq_n} and \ref{fig:alt_qq_g}, which display Q-Q plots
of the $p$-values under the null for Normal and Gamma margins, respectively.
Recall from Figures~\ref{fig:qq_n} and \ref{fig:qq_g} that the cubic root 
setting holds its size quite well with small $n$ for $|\tau| \leq 0.25$,
whereas achieving nominal size for $|\tau| \geq 0.5$ require
$n > 200$, and for $|\tau| \geq 0.75$ require $n > 800$. The automatic
selection shows similar limitations for $|\tau| > 0.5$, where it does
not hold its size. Moreover, deviations from the diagonal line appear
larger for negative $\tau$, likely due to the high proportion of
occurrence of overly large block sizes. For example, while the cubic
root setting held its size well at $\tau = -0.25$ with small~$n$, the
automatic selection does not. At the same time, under $\tau = 0$ or
$\tau = 0.25$, the method with block size selected by
\citep{politis2004automatic} maintains reasonable size for moderately
positively dependent series.

Figure~\ref{fig:alt_rr} shows the power results under automatic selection.
When compared to Figure~\ref{fig:rr}, the two settings exhibit similar power
for $|\tau| \leq 0.5$, with the automatic selection sometimes yielding higher
rejection rates, particularly for smaller negatively dependent samples.
Overall, while the automatic selection from \citep{politis2004automatic}
performs reasonably well in certain settings, we recommend caution when using
it under negative~$\tau$ and smaller sample sizes, where maintaining nominal
size may be more difficult. In such cases, it may be sensible to apply a more
restrictive rule when setting the final block size---for example, using
$\min \{\sqrt{n}, \hat{l}\}$.
